### 2024-08-22 paper.tex
one direction of alternative characterization

\par First, we provide an alternative characterization of \(B_{I, (\rho_i)}\).
Let \(B_{I, (\rho_i)}'\) be the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
\begin{itemize}
    \item For all \(k \in \{1, ..., r\}\), \(p_i = \rho_i\).
    \item For \(i \notin I\), let \(S = \{k \in \{1, ..., r\} : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
    If \(S = \emptyset\), then \(p_i \leq \lambda_i - q_{i_0}\).
    Otherwise, \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\), where \(k = \min S\).
\end{itemize}
\begin{lemma}\label{alternative_bs}
    \(B_{I, (\rho_i)} = B_{I, (\rho_i)}'\).
\end{lemma}
\begin{proof}
    First we show that \(B_{I, (\rho_i)} \subseteq B_{I, (\rho_i)}'\).
    Let \(b \in B_{I, (\rho_i)}\).
    It is clear that \(\forall i \in I. \; p_i = \rho_i\).
    Now, I claim that for every \(s \in \{0, ..., r\}\), either 
    So, let \(i \notin I\), and let \(S = \{k : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
    We have two cases: either \(S\) is empty, or not.
    \par If \(S\) is empty

    and let \(k = \min S\).
    We need to show that \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\).
    That is, need to show that \(\)
    \par Let \(l \in \{0, ..., r\}\), and suppose \(q_i < q_{i_l}\).
    Then, since \(\max_{j : q_j < q_{i_l}} p_j = p_{i_{l + 1}}\), we have \(p_i \leq p_{i_{l + 1}}\).
    This implies that 
\end{proof}

>>>>

\par First, we provide an alternative characterization of \(B_{I, (\rho_i)}\).
Let \(B_{I, (\rho_i)}'\) be the set of \(b \in \mathbb{C}^m\) satisfying the following conditions.
\begin{itemize}
    \item For all \(k \in \{1, ..., r\}\), \(p_i = \rho_i\).
    \item For \(i \notin I\), let \(S = \{k \in \{1, ..., r + 1\} : q_{i_{k - 1}} + p_{i_k} > \lambda_i\}\).
    If \(S = \emptyset\), then \(p_i \leq \lambda_i - q_{i_0}\).
    If \(r + 1 \in S\), then \(p_i \leq p_{i_{r + 1}}\).
    Otherwise, \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\), where \(k = \max S\).\footnote{I could remove the edge cases if I define \(q_{i_{-1}}\) and \(q_{i_{r + 1}}\)... ah, maybe a bit less drastically, I can say something like min(complement of S) instead of max(S)}
\end{itemize}
\begin{lemma}\label{alternative_bs}
    \(B_{I, (\rho_i)} = B_{I, (\rho_i)}'\).
\end{lemma}
\begin{proof}
    First we show that \(B_{I, (\rho_i)} \subseteq B_{I, (\rho_i)}'\).
    Let \(b \in B_{I, (\rho_i)}\).
    It is clear that \(\forall i \in I. \; p_i = \rho_i\).
    \par First suppose \(S = \emptyset\).
    Then if we had \(q_i < q_{i_0}\), this would entail \(p_i \leq \max_{j : q_j < q_{i_0}} = p_{i_1}\).
    But then \(\lambda_i = p_i + q_i < q_{i_0} + p_{i_1}\), contradicting that \(1 \notin S\).
    Hence \(q_i \geq q_{i_0}\), and therefore \(p_i \leq \lambda_i - q_{i_0}\).
    \par Now suppose \(r + 1 \in S\).
    Then \(q_{i_r} = q_{i_r} + p_{i_{r + 1}} > \lambda_i\).
    Then certainly \(q_i < q_{i_r}\), and therefore \(p_i \leq \max_{j : q_j < q_{i_r}} p_j = p_{i_{r + 1}}\).
    \par If we are in neither of those cases, let \(k = \max S\).
    We have \(q_{i_k} + p_{i_{k + 1}} \leq \lambda_i\).
    Suppose we had \(q_i < q_{i_k}\).
    Then \(p_i \leq \max_{j : q_j < q_{i_k}} p_j = p_{i_{k + 1}}\).
    But then \(p_i + q_i < q_{i_k} + p_{i_{k + 1}} \leq \lambda_i\), which is a contradiction since \(k + 1 \notin S\).
    Thus \(q_i \geq q_{i_k}\).
    Now, we have two cases: either \(q_i \geq q_{i_{k - 1}}\), or \(q_i < q_{i_{k - 1}}\).
    In the second case, we see that \(p_i \leq p_{i_k}\).
    In the first, recall we also have \(q_{i_{k - 1}} + p_{i_k} > \lambda_i = p_i + q_i\) (since \(k \in S\)), so \(p_{i_k} > p_i\).
    So, in any case, we have \(q_i \geq q_{i_k}\) and \(p_i \leq p_{i_k}\); or, in other words, \(p_i \leq \min(p_{i_k}, \lambda_i - q_{i_k})\).
    \par Hence \(b \in B'_{I, (\rho_i)}\), and we see that \(B_{I, (\rho_i)} \subseteq B'_{I, (\rho_i)}\).
    Now we show the opposite inclusion.
    Let \(b \in B_{I, (\rho_i)}\).
    Again it is clear that \(\forall i \in I. \; p_i = \rho_i\).
    \par Let \(k \in \{0, ..., r\}\).
    I need to show that \(p_{i_{k + 1}} = \max_{j : q_j < q_{i_k}} p_j\).
    It suffices to show that for every \(i \in I\), either \(p_i \leq p_{i_{k + 1}}\) or \(q_i \geq q_{i_k}\).
    Agh.  continue here.
\end{proof}
